|

### 2025-01-26 doc/paper.qmd
streamline paper

The paper is structured into sections corresponding to Tasks 1–3 (@sec-task1, @sec-task2, @sec-task3), each detailing the research design choices and assumptions, documenting the replication steps, and analyzing the replication results for the respective segment. @sec-task1 follows an exact replication approach by replicating key tables and figures from the original study using US data (1972–2006) to establish baseline results. @sec-task2 extends the analysis through empirical generalization, applying the same methodology to 2007–2023 US data to compare how results evolve over time. @sec-task3 employs a generalization and extension approach by applying the methodology to a non-US country, requiring adjustments for different databases and market structures. This framework aligns with the replication taxonomy outlined by @salterio_replication_2022. Finally, @sec-task4 sketches the survey design as a non-archival study that allows evaluating the key findings of the seminal paper, following Bloomfield’s (2016) triangulation principle. The concluding remarks are provided in @sec-conclusion.

@@

Task 1 is the most comprehensive, replicating key tables and figures from @ball_how_2008 using daily US stock return data (1972–2006) to establish baseline results. This ensures alignment with the original findings before extending the analysis in later tasks. By reconstructing Table 1 (Panel A), Table 2 (all panels), and Figure 1 (all panels), this task evaluates the robustness of the original results and identifies potential discrepancies, offering insights into data consistency, methodology, and market dynamics over the examined period. The use of daily CRSP data is essential for capturing short-term stock price movements around earnings announcements, ensuring precise event window calculations.

-----
The project uses data from the Audit Analytics database on Transparency Reports via Wharton Research Data Services (WRDS) for the year 2021, covering PIEs across EU countries. The replication closely follows the methodology outlined by @EC_Report_2024. It focuses on three key market concentration measures: the market share of the Big 4 audit firms, the CR4 market share for the largest four firms in each country, and the 10KAP market share, which includes the Big 4 and additional major networks. These measures provide a detailed assessment of audit firm dominance and competition, offering valuable insights into the structure and dynamics of the statutory audit market in Europe.

The analysis involves gathering and filtering Transparency Report data, identifying relevant PIEs and EU countries, and calculating the Big 4, CR4, and 10KAP market shares for each country as well as at the EU level. Explicit assumptions were made whenever the document by @EC_Report_2024 was unclear on how to proceed. The entire Python computation code for market share calculations is available in `code/python/do_analysis.py` for detailed review if necessary. This paper focuses on the replication process, presenting visualizations, and discussing the results.

The replicated figure from original report by @EC_Report_2024 is shown below, followed by the research design choices and assumptions in @sec-research_design_assumptions, documentation of the replication steps in @sec-replication_steps, a detailed results comparison in @sec-results, and concluding remarks in @sec-conclusion.

@fig-market-shares illustrates the market shares of audit firms — Big 4, CR4, and 10KAP — for the number of PIE statutory audits conducted in 2021. Countries are sorted in a specific order reflecting the replication of Figure 3 from the European Commission’s 2024 report. The discussion of replication findings is presented in @sec-results.
```{python}
#| label: fig-market-shares
#| fig-cap: "Replicated Figure 3: Audit Firms' Market Shares in the EU for 2021"
#| fig-align: center
#| echo: false

@@

## Research Design Choices and Assumptions {#sec-research_design_assumptions1}
I impose the following assumptions to ensure clarity and consistency where @ball_how_2008 do not provide explicit guidance:

@@

------
The aim of Assignment I is to replicate a specific empirical figure (Figure 3) from the report by @EC_Report_2024. This figure involves analyzing the market shares of audit firms (Big 4, CR4, and 10KAP) across EU countries and at the EU level for PIE statutory audits conducted in 2021. The replication process includes data loading, preparation, and cleaning, followed by the computation and visualization of market concentration measures. For Assignment I, I pulled data from the Audit Analytics database via WRDS and used the Python programming language to carry out the empirical analysis. Visual Studio Code was used as the Integrated Development Environment (IDE) for writing, debugging, and optimizing the Python code.

The replication is based on data pulled from the Audit Analytics Transparency Reports database, specifically from `audit_europe.feed76_transparency_reports` table, which was filtered and aggregated for the analysis. The table offers Transparency Reports published annually by audit firms based in the EEA and Switzerland, along with the names of all entities listed in each audit firm’s Transparency Reports [@WRDS_Audit_Analytics_Transparency_Reports].

Following @EC_Report_2024, I focus the analysis on statutory audits conducted for the fiscal year 2021, ensuring that the data accurately reflects the audit market structure in the EU as specified in the original report. The replication aims to mirror the research design as closely as possible with the available data.

In addition, I impose the following assumptions to ensure clarity and consistency where the report by @EC_Report_2024 does not provide explicit guidance:

@@

By following the steps provided in @sec-replication_steps and adhering to the assumptions made, I successfully replicated the analysis and produced the required figure. A thorough step-by-step approach, with each step clearly documented, helped to understand and verify the outputs.

@@

@@

Step 2: Data Preparation {#sec-step2_preparation}
The raw Transparency Report dataset initially contained 13,385 observations, representing entries for the year 2021. To ensure consistency with @EC_Report_2024, the abbreviation 'GR' for Greece was replaced with 'EL' in the trans_report_auditor_state field, affecting 188 rows.

>>>>

The paper is structured into sections corresponding to Tasks 1–3 (@sec-task1, @sec-task2, @sec-task3), each detailing the research design choices and assumptions, documenting the replication steps, and analyzing the replication results for the respective segment. @sec-task1 follows an exact replication approach by replicating key tables and figures from the original study using US data (1972–2006) to establish baseline results. @sec-task2 extends the analysis through empirical generalization, applying the same methodology to 2007–2023 US data to compare how results evolve over time. @sec-task3 employs a generalization and extension approach by applying the methodology to a non-US country, requiring adjustments for different databases and market structures. This framework aligns with the replication taxonomy outlined by @salterio_replication_2022. Finally, @sec-task4 sketches the survey design as a non-archival study that allows evaluating the key findings of the seminal paper, following Bloomfield’s (2016) triangulation principle. The concluding remarks are provided in @sec-conclusion.  The entire Python computation code for return calculations is available in `code/python/do_analysis.py` for detailed review if necessary. This paper focuses on the replication process, presenting visualizations, and discussing the results.

@@

Task 1 is the most comprehensive, replicating the methodology of key tables and figures from @ball_how_2008 using daily US stock return data (1972–2006) to establish baseline results. This ensures alignment with the original findings before extending the analysis in later tasks. By reconstructing Table 1 (Panel A), Table 2 (all panels), and Figure 1 (all panels), this task evaluates the robustness of the original results and identifies potential discrepancies, offering insights into data consistency, methodology, and market dynamics over the examined period. The use of daily CRSP data is essential for capturing short-term stock price movements around earnings announcements, ensuring precise event window calculations.

-----
##The analysis involves gathering and filtering Transparency Report data, identifying relevant PIEs and EU countries, and calculating the Big 4, CR4, and 10KAP market shares for each country as well as at the EU level.

##@fig-market-shares illustrates the market shares of audit firms — Big 4, CR4, and 10KAP — for the number of PIE statutory audits conducted in 2021. Countries are sorted in a specific order reflecting the replication of Figure 3 from the European Commission’s 2024 report. The discussion of replication findings is presented in @sec-results.
```{python}
#| label: fig-market-shares
#| fig-cap: "Replicated Figure 3: Audit Firms' Market Shares in the EU for 2021"
#| fig-align: center
#| echo: false

@@

## Research Design Choices and Assumptions {#sec-research_design_assumptions1}
Following @ball_how_2008, I focus the analysis on earnings announcements and stock returns from 1972 to 2006, ensuring that the data accurately reflects the original study’s methodology and findings. The replication aims to mirror the research design as closely as possible with the available data, maintaining consistency in sample selection, event window definitions, and return calculations.

In addition, I impose the following assumptions to ensure clarity and consistency where @ball_how_2008 do not provide explicit guidance:

@@

4. As in the original paper, firm-years are selected based on available stock return data in CRSP. While @ball_how_2008 restrict the sample to firms with at least 240 trading days per year, I follow the course guidance and do not apply this restriction, allowing for a slightly larger sample size. This adjustment should be considered when interpreting differences from the original study.

By following the steps outlined in @sec-replication_steps1 and adhering to the assumptions made, I successfully replicated Table 1 (Panel A), Table 2 (all panels), and Figure 1 (all panels) from @ball_how_2008. A thorough step-by-step approach, with each step clearly documented, helped to understand and verify the outputs.

------

@@

@@

##The replication process includes data loading, preparation, and cleaning, followed by the computation and visualization of market concentration measures. For Assignment I, I pulled data from the Audit Analytics database via WRDS and used the Python programming language to carry out the empirical analysis. Visual Studio Code was used as the Integrated Development Environment (IDE) for writing, debugging, and optimizing the Python code.

##The replication is based on data pulled from the Audit Analytics Transparency Reports database, specifically from `audit_europe.feed76_transparency_reports` table, which was filtered and aggregated for the analysis. The table offers Transparency Reports published annually by audit firms based in the EEA and Switzerland, along with the names of all entities listed in each audit firm’s Transparency Reports [@WRDS_Audit_Analytics_Transparency_Reports].

@@

Step 2: Data Preparation
The raw Transparency Report dataset initially contained 13,385 observations, representing entries for the year 2021. To ensure consistency with @EC_Report_2024, the abbreviation 'GR' for Greece was replaced with 'EL' in the trans_report_auditor_state field, affecting 188 rows.
